Psyc 601 Multivariate Statistics Project

### 2013-08-12 writeups/proposal/proposal.tex
Mon commit
Former-commit-id: 187bbab021a30daea008f2f7813a3bcf3392fa9d [formerly 6258a37350ba2696ecb1952eca6a9352e6e950b6]
Former-commit-id: 6179e69077c912be9041b6a093c8ecf956e28a2f

@@

@@

@@

\section{Hashtag Prediction}

@@

\subsubsection{Netflix}

\subsubsection{Facebook}

\subsubsection{Twitter}

@@

@@

@@

@@

TODO: Issue of scale.

@@

@@

@@

@@

@@

@@

>>>>

TODO: Identifying user's goals when searching social media sites is an open research problem \cite{Rose2004}

TODO: Researchers are currently looking for ways to automate the task \cite{Lee2005}, \cite{Jansen2008}

TODO: Hashtags are an additional view of a user's goals when generating content on a site, and can help in this automation.
TODO: These hashtags relate to user's goals and interests because they are human-generated content; a form of human-based document tagging \cite{Chang2010}
TODO: People are also using hashtags as an information source on social media cites \cite{Diakopoulos2010} \cite{Kwak2010}

TODO: Natural question to ask is how can we build human-computer systems that help connect users to these hashtag information sources.

TODO: Co-occurence-based modeling is a potentially useful approach. \cite{Efron2010}

TODO: Challenging domain due to time constraints on information. \cite{Bauer2012}

TODO: Useful problem since real-time search on social media sites is growing \cite{Jansen2011}

@@

TODO: Extending work from \cite{Rutledge2008}

TODO: Can user prior be represented in vector-based memory systems?

TODO: Can word order be represented in ACT-R?

@@

TODO: Comparison to global lifetime of a hashtag \cite{Tsur2012}

@@

\subsubsection{Task Domain}

TODO: StackOverflow and Twitter; large scale, hashtag prediction, etc.

\section{Prior Work on Hashtag Prediction}

\subsection{StackOverflow}

TODO: \cite{Kuo2011}

\subsection{Twitter}

FIXME: Find cite for twitter hashtag prediction

@@

FIXME: Find cites for recommendation systems.

@@

\cite{Anderson2004}

@@

TODO: Introduce PMI \cite{Farahat2004}

TODO: Comparison to ACT-R: Virtually equivalent for large corpora \cite{Farahat2004}

\subsection{Scaling the Equations}

\cite{Douglass2010}

TODO: SNIF-ACT \cite{Fu2007} \cite{Pirolli2003}

@@

TODO: Summarize \cite{Landauer1997}

@@

TODO: Performance and issue of scale. \cite{Budiu2007}

@@

TODO: Summarize \cite{Plate1995}

@@

TODO: Sumarize Jones' model \cite{Jones2007}

@@

TODO: Summarize \cite{Sahlgren2008}

\subsection{Comparison between BEAGLE and Random Permutations}

TODO: Summarize \cite{Recchia2010}

@@

FIXME: Get citation.

\section{Comparison of Vector-based Models and ACT-R}

TODO: Summarize \cite{Rutledge2007}

TODO: This approach can be used to model the fan effect \cite{Rutledge2008}

TODO: However, there are open issues that need to be addressed:
TODO: Can user prior be represented in vector-based memory systems?
TODO: Can word order be represented in ACT-R?
TODO: Do they both scale?

@@

\cite{DataDump2013}

@@

\subsection{Tokenizing and Lemmetizing Text}

TODO: Python NLP toolkit \cite{Bird2009}

\subsection{Stop Words and Entropy Weighting}

TODO: Explore entropy weighting instead of stop word removal \cite{Dumais1991}
